A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-10-09 paper/paper.abstract.tex
Update paper.abstract.tex
abstract edits

Scheduling of personnel in a hospital environment is vital to improving the service provided to patients and balancing the workload assigned to clinicians. Many approaches have been tried and successfully applied to generate efficient schedules in such settings. However, due to the computational complexity of the scheduling problem in general, most approaches resort to heuristics to find a non-optimal solution in a reasonable amount of time. We designed an integer linear programming formulation to find an optimal schedule in a clinical division of a hospital. Our formulation mitigates computational complexity issues by maintaining a minimal set of constraints, yet still provides the flexibility necessary to adapt it to a variety of clinical divisions. \\

>>>>

Scheduling of personnel in a hospital environment is vital to improving the service provided to patients and balancing the workload assigned to clinicians. Many approaches have been tried and successfully applied to generate efficient schedules in such settings. However, due to the computational complexity of the scheduling problem in general, most approaches resort to heuristics to find a non-optimal solution in a reasonable amount of time. We designed an integer linear programming formulation to find an optimal schedule in a clinical division of a hospital. Our formulation mitigates issues related to computational complexity via a minimum the set of constraints, yet retains sufficient flexibility so that it can be adapted to a variety of clinical divisions. \\
